---
title: "WiSTEM 2022 - 2023"
subtitle: "Attendance Analysis"

format:
  html:
    toc: true
    embed-resources: true
    echo: false
    link-external-newwindow: true
execute:
  warning: false
  message: false

from: markdown+emoji  
editor: 
  markdown: 
    wrap: 72
---

```{r}
#| label: load-packages

library(tidyverse)
library(patchwork)
library(readr)
library(kableExtra)

set.seed(1968)
```

```{r}
#| label: load-data-sets

data <- read_csv(file = "data/processed/wistem_attendance_clean.csv")

data$date <- factor(data$date, levels = c("May 12th", "Apr 28th", "Apr 14th", "Mar 31st", "Mar 3rd", "Feb 24th", "Feb 10th", "Jan 27th", "Dec 16th", "Dec 2nd", "Nov 18th", "Oct 28th", "Oct 14th", "Sep 30th")) 
```

# Background

**WiSTEM:** In total, there were 17 overall WiSTEM meetings held throughout the 2022-2023 academic school year. However, there were 13 meetings with attendance data and 13 meetings with exit slip data. Some of these overlap in missing both attendance and exit slip data. 

## Students Also in WiENG

```{r}
#| label: overlap-students

# Load Data
wieng_data <- read_csv(file = "data/processed/wieng_attendance_clean.csv")
wistem_data <- read_csv(file = "data/processed/wistem_attendance_clean.csv")

# WiENG 
wieng_names <- wieng_data %>% # 32 unique students
  select(name, student_id) %>%
  unique()

wieng_unique_students <- wieng_names %>%
  nrow()

# WiSTEM
wistem_names <- wistem_data %>% # 138 unique students
  select(name, student_id) %>%
  unique()

wistem_unique_students <- wistem_names %>%
  nrow()

# Overlapping
overalping_students <- dplyr::semi_join(wieng_names, wistem_names, "student_id")
num_overlap_student <- overalping_students %>%
  nrow()

## Percentage
wieng_overlap_percent <- round((num_overlap_student / wieng_unique_students) * 100, 2)
wistem_overlap_percent <- round((num_overlap_student / wistem_unique_students) * 100, 2)
```

WiENG was a program created after the start of WiSTEM with a focus on engineering. Therefore, some students started to go to both WiSTEM and WiENG meetings. Overall, in the 2022 - 2023 academic school year, `r num_overlap_student` unique students attended both meetings. There were `r wieng_unique_students` total unique WiENG students, meaning `r wieng_overlap_percent` percent of the total population. Meanwhile, there were `r wistem_unique_students` total unique WiENG students, meaning `r wistem_overlap_percent` percent of the total population.

## Attendance Per Meeting
 
```{r}
#| label: attnd-per-meeting

# Graph
ggplot(data = data, mapping = aes(y = date)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat='count', aes(label=..count..), position = position_stack(vjust = 0.9)) +
  labs(
    title = "Number of Attendance Per Meeting", 
    subtitle = "With Repeats",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Students", 
    y = "Meeting Date"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Attendance Per Meeting
```{r}
# Table
data %>%
  count(date) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  rename(num_students = n) %>%
  kbl(caption = "Number of Attendance Per Meeting") %>%
  kable_styling()
```
:::

## Attendance Per Month
 
```{r}
#| label: attnd-per-month

data_split_date <- data[c('month', 'day')] <- str_split_fixed(data$date, ' ', 2) %>%
  as_tibble() %>%
  rename(month = V1, day = V2) %>%
  mutate(day = substr(day, 1, 2))

data_split_date$month <- factor(data_split_date$month, levels = c("May", "Apr", "Mar", "Feb", "Jan", "Dec", "Nov", "Oct", "Sep")) 

# Graph
ggplot(data = data_split_date, mapping = aes(y = month)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat='count', aes(label=..count..), position = position_stack(vjust = 0.9)) +
  labs(
    title = "Number of Attendance In Each Month", 
    subtitle = "With Repeats",
    x = "Number of Students", 
    y = "Month"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Attendance Per Month
```{r}
# Table
data_split_date %>%
  count(month) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  rename(num_students = n) %>%
  kbl(caption = "Number of Attedance In Each Month") %>%
  kable_styling()
```
:::

## Attendance Per Topic
 
```{r}
#| label: attnd-per-topic

# Graph
ggplot(data = data, mapping = aes(x = topic)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat='count', aes(label=..count..), position = position_stack(vjust = 0.5)) +
  labs(
    title = "Total Attendance Per Topic Type", 
    subtitle = "With Repeats",
    caption = "Source: WiSTEM 2022-2023",
    x = "Meeting Topic", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Attendance Per Topic
```{r}
# Table
topic_attn_total <- data %>%
  count(topic) %>%
  rename(total = n)

topic_attn_total %>%
  mutate(
    proportion = total / sum(total), 
    percent = (total / sum(total)) * 100 
  ) %>%
  kbl(caption = "Total Attendance Per Topic Type") %>%
  kable_styling()
```
:::

## Average Attendance Per Topic
 
```{r}
#| label: avg-attnd-per-topic

topic_meeting_total <- data %>%
  select(date, topic) %>%
  unique() %>%
  count(topic) %>%
  rename(meeting_count = n)

avg_topic_data <- full_join(topic_meeting_total, topic_attn_total) %>%
  mutate(
    meeting_avg = total / meeting_count, 
    total_avg = 630 / 14
    )

# Graph
ggplot(data = avg_topic_data, mapping = aes(x = topic, y = meeting_avg)) + 
  geom_col(color = "azure4", fill = "lightcyan2") + 
  labs(
    title = "Average Attendance per Meeting Topic Compared to Overall Average", 
    subtitle = "With Repeats",
    caption = "Source: WiSTEM 2022-2023",
    x = "Meeting Topic", 
    y = "Average Number of Students"
    ) + 
  geom_hline(yintercept = 630 / 14) +
  geom_text(aes(label = meeting_avg), position = position_stack(vjust = 0.5)) +
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Average Attendance Per Topic
```{r}
# Table
mutate_better_than <- function(avg_topic_data) {
  avg_topic_data %>%
    mutate(benchmark = ifelse(meeting_avg > total_avg, "yes", "no"))
}

avg_topic_data <- mutate_better_than(avg_topic_data)

avg_topic_data %>%
  kbl(caption = "Average Attendance Per Meeting Topic") %>%
  kable_styling()
```
:::

# Individual Attendance

## Number of Meetings Attended
 
```{r}
#| label: num-meetings

indiv_atten <- data %>%
  count(name) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100
  ) %>% 
  arrange(desc(percent))

cat_indiv_atten <- indiv_atten %>%
  count(n) %>%
  rename(num_meetings = n, num_students = nn) %>%
  mutate(
    proportion = num_students / sum(num_students), 
    percent = proportion * 100
  ) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    num_students = as_factor(num_students)
    )

# Graph
ggplot(data = cat_indiv_atten, mapping = aes(x = num_meetings, y = num_students)) + 
  geom_col(color = "azure4", fill = "lightcyan2") + 
  geom_text(aes(label = num_students), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Number of Meetings Attended by Unique Students", 
    subtitle = "Unique",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()

# Average Number
indiv_atten %>%
  rename(num_students = n) %>%
  summarize(
    min = min(num_students), 
    median = median(num_students), 
    mean = mean(num_students), 
    std_dev = sd(num_students),
    max = max(num_students), 
    range = max - min
  ) %>%
  kbl(caption = "Summary of Number of Meetings Attended") %>%
  kable_styling()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended
```{r}
# Table
cat_indiv_atten %>% 
  arrange(desc(percent)) %>%
  kbl(caption = "Number of Meetings Attended by Unique Students") %>%
  kable_styling()
```
:::

## Only One Meeting Attended
 
```{r}
#| label: one-meeting-attnd

meeting_one_attend <- data %>%
  filter(num_meetings == 1) %>%
  select(date, topic, num_meetings) %>%
  count(date) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  )

# Graph
ggplot(data = meeting_one_attend, mapping = aes(x = date, y = num_students)) + 
  geom_col(color = "azure4", fill = "lightcyan2") + 
  labs(
    title = "Number of Students Per Meeting Who Attended One Meeting", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Meeting Date", 
    y = "Number of Students"
    ) + 
  geom_text(aes(label = num_students), position = position_stack(vjust = 0.5)) +
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Only One Meeting Attended
```{r}
# Table
meeting_one_attend %>%
  kbl(caption = "Number of Student Per Meetings Who Only Attended Once") %>%
  kable_styling()
```
:::

## One Meeting and Federal Race
 
```{r}
#| label: fed-race-one-meeting-attnd

one_meeting_fed_race <- data %>%
  filter(num_meetings == 1) %>%
  select(num_meetings, federal_race) %>%
  mutate(num_meetings = as_factor(num_meetings)) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  )

# Graph for All
unique_colors <- c("lightpink2", "darkseagreen2", "lavender", "khaki", "lightcyan2")

ggplot(data = one_meeting_fed_race, mapping = aes(x = federal_race, y = num_students, fill = federal_race)) +
  geom_col() + 
  scale_fill_manual(values = unique_colors) +
  geom_text(aes(label = paste0(round(percent, 1), "%")), position = position_stack(vjust = 0.5)) +
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  labs(
    title = "Number of Students Per Meeting Who Attended One Meeting", 
    subtitle = "By All Federal Race Categories (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  theme_minimal()

# Considering White and Non-White
one_meeting_fed_race_two <- data %>%
  filter(num_meetings == 1) %>%
  select(num_meetings, federal_race) %>%
  mutate(num_meetings = as_factor(num_meetings))

one_meeting_fed_race_two$federal_race <- recode(one_meeting_fed_race_two$federal_race, "Asian" = "Non-White")
one_meeting_fed_race_two$federal_race <- recode(one_meeting_fed_race_two$federal_race, "Black" = "Non-White")
one_meeting_fed_race_two$federal_race <- recode(one_meeting_fed_race_two$federal_race, "LatinX" = "Non-White")
one_meeting_fed_race_two$federal_race <- recode(one_meeting_fed_race_two$federal_race, "T.M.O." = "Non-White")

one_meeting_fed_race_two <- one_meeting_fed_race_two %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  )

## Graph
ggplot(data = one_meeting_fed_race_two, mapping = aes(x = federal_race, y = num_students, fill = federal_race)) +
  geom_col() + 
  scale_fill_manual(values = unique_colors) +
  geom_text(aes(label = paste0(round(percent, 1), "%")), position = position_stack(vjust = 0.5)) +
  labs(
    title = "Number of Students Per Meeting Who Attended One Meeting",
    subtitle = "By White and Non-White Students (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race and Only One Meeting Attended
```{r}
# Table
one_meeting_fed_race %>%
  kbl(caption = "Federal Race and Students Who Attended One Meeting") %>%
  kable_styling()

one_meeting_fed_race_two %>%
  kbl(caption = "White & Non-White and Students Who Attended One Meeting") %>%
  kable_styling()
```
:::

## One Meeting and Graduation Year

```{r}
#| label: grad-year-one-meeting-attnd

one_meeting_grad_year <- data %>%
  filter(num_meetings == 1) %>%
  select(num_meetings, graduation_year) %>%
  mutate(graduation_year = as_factor(graduation_year)) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  )

# Graph
ggplot(data = one_meeting_grad_year, mapping = aes(x = graduation_year, y = num_students, fill = graduation_year)) +
  geom_col() + 
  scale_fill_manual(values = unique_colors) +
  geom_text(aes(label = num_students), position = position_stack(vjust = 0.5)) +
  labs(
    title = "Number of Students Per Meeting Who Attended One Meeting", 
    subtitle = "By Graduation Year (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Year and Only One Meeting Attended
```{r}
# Table
one_meeting_grad_year %>%
  kbl(caption = "Graduation Year and Students Who Attended One Meeting") %>%
  kable_styling()
```
:::

## One Meeting and Topic

```{r}
#| label: topic-one-meeting-attnd

one_meeting_topic <- data %>%
  filter(num_meetings == 1) %>%
  select(num_meetings, topic) %>%
  mutate(topic = as_factor(topic)) %>%
  count(topic) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  )

# Graph
ggplot(data = one_meeting_topic, mapping = aes(x = topic, y = num_students, fill = topic)) +
  geom_col() + 
  scale_fill_manual(values = unique_colors) +
  geom_text(aes(label = num_students), position = position_stack(vjust = 0.5)) +
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  labs(
    title = "Number of Students Per Meeting Who Attended One Meeting", 
    subtitle = "By Topic (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Topic", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Topic and Only One Meeting Attended
```{r}
# Table
one_meeting_grad_year %>%
  kbl(caption = "Topic and Students Who Attended One Meeting") %>%
  kable_styling()
```
:::

# Distribution Per Meeting

## September 30, 2022
```{r}
#| label: sep-30-dist

sep_30_data <- data %>%
  filter(date == "Sep 30th") %>%
  select(date, topic, num_meetings, graduation_year, federal_race, iep, program_504, esl) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    graduation_year = as_factor(graduation_year), 
    federal_race = as_factor(federal_race)
    )
```

```{r}
#| label: sep-30-num-meetings

# Graph
ggplot(data = sep_30_data, mapping = aes(x = num_meetings)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Attendance Distribution By Number of Meetings Attended", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended for September 30th
```{r}
# Table
sep_30_data %>%
  select(date, num_meetings) %>%
  count(num_meetings) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Number of Meetings Attended") %>%
  kable_styling()
```
:::

```{r}
#| label: sep-30-grad-year

# Graph
sep_30_grad <- ggplot(data = sep_30_data, mapping = aes(x = graduation_year, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()
```

```{r}
#| label: sep-30-race

# Graph
sep_30_race <- ggplot(data = sep_30_data, mapping = aes(x = federal_race, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Race", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()

sep_30_grad + sep_30_race
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Race for September 30th
```{r}
# Table
sep_30_data %>%
  select(date, graduation_year) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Graduation Year") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race for September 30th
```{r}
# Table
sep_30_data %>%
  select(date, federal_race) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Distribution By Federal Race") %>%
  kable_styling()
```
:::

```{r}
#| label: sep-30-extra-charac

sep_30_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(2, 46, 6, 42, 1, 47)
)

# Graph
ggplot(data = sep_30_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics for September 30th
```{r}
# Table
sep_30_charac_table %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::

## October 14, 2022
```{r}
#| label: oct-14-dist

oct_14_data <- data %>%
  filter(date == "Oct 14th") %>%
  select(date, topic, num_meetings, graduation_year, federal_race, iep, program_504, esl) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    graduation_year = as_factor(graduation_year), 
    federal_race = as_factor(federal_race)
    ) %>%
  filter(!is.na(federal_race), !is.na(graduation_year), !is.na(iep), !is.na(program_504), !is.na(esl))
```

```{r}
#| label: oct-14-num-meetings

# Graph
ggplot(data = oct_14_data, mapping = aes(x = num_meetings)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Attendance Distribution By Number of Meetings Attended", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended for October 14th
```{r}
# Table
oct_14_data %>%
  select(date, num_meetings) %>%
  count(num_meetings) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Number of Meetings Attended") %>%
  kable_styling()
```
:::

```{r}
#| label: oct-14-grad-year

# Graph
oct_14_grad <- ggplot(data = oct_14_data, mapping = aes(x = graduation_year, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()
```

```{r}
#| label: oct-14-race

# Graph
oct_14_race <- ggplot(data = oct_14_data, mapping = aes(x = federal_race, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Race", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()

oct_14_grad + oct_14_race
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Race for October 14th
```{r}
# Table
oct_14_data %>%
  select(date, graduation_year) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Graduation Year") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race for October 14th
```{r}
# Table
oct_14_data %>%
  select(date, federal_race) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Federal Race") %>%
  kable_styling()
```
:::

```{r}
#| label: oct-14-extra-charac

oct_14_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(2, 32, 7, 27, 3, 31)
)

# Graph
ggplot(data = oct_14_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics for October 14th
```{r}
# Table
oct_14_charac_table %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::

## October 28, 2022
```{r}
#| label: oct-28-dist

oct_28_data <- data %>%
  filter(date == "Oct 28th") %>%
  select(date, topic, num_meetings, graduation_year, federal_race, iep, program_504, esl) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    graduation_year = as_factor(graduation_year), 
    federal_race = as_factor(federal_race)
    ) %>%
  filter(!is.na(federal_race), !is.na(graduation_year), !is.na(iep), !is.na(program_504), !is.na(esl))
```

```{r}
#| label: oct-28-num-meetings

# Graph
ggplot(data = oct_28_data, mapping = aes(x = num_meetings)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Number of Meetings Attended", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended for October 28th
```{r}
# Table
oct_28_data %>%
  select(date, num_meetings) %>%
  count(num_meetings) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Number of Meetings Attended") %>%
  kable_styling()
```
:::

```{r}
#| label: oct-28-grad-year

# Graph
oct_28_grad <- ggplot(data = oct_28_data, mapping = aes(x = graduation_year, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

```{r}
#| label: oct-28-race

# Graph
oct_28_race <- ggplot(data = oct_28_data, mapping = aes(x = federal_race, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Race", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()

oct_28_grad + oct_28_race
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Race for October 28th
```{r}
# Table
oct_28_data %>%
  select(date, graduation_year) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Graduation Year") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race for October 28th
```{r}
# Table
oct_28_data %>%
  select(date, federal_race) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Federal Race") %>%
  kable_styling()
```
:::

```{r}
#| label: oct-28-extra-charac

oct_28_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(3, 44, 8, 39, 2, 45)
)

# Graph
ggplot(data = oct_28_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics for October 28th
```{r}
# Table
oct_28_charac_table %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::

## November 18, 2022
```{r}
#| label: nov-18-dist

nov_18_data <- data %>%
  filter(date == "Nov 18th") %>%
  select(date, topic, num_meetings, graduation_year, federal_race, iep, program_504, esl) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    graduation_year = as_factor(graduation_year), 
    federal_race = as_factor(federal_race)
    ) %>%
  filter(!is.na(federal_race), !is.na(graduation_year), !is.na(iep), !is.na(program_504), !is.na(esl))
```

```{r}
#| label: nov-18-num-meetings

# Graph
ggplot(data = nov_18_data, mapping = aes(x = num_meetings)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Number of Meetings Attended", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended for November 18th
```{r}
# Table
nov_18_data %>%
  select(date, num_meetings) %>%
  count(num_meetings) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Number of Meetings Attended") %>%
  kable_styling()
```
:::

```{r}
#| label: nov-18-grad-year

# Graph
nov_18_grad <- ggplot(data = nov_18_data, mapping = aes(x = graduation_year, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

```{r}
#| label: nov-18-race

# Graph
nov_18_race <- ggplot(data = nov_18_data, mapping = aes(x = federal_race, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Race", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()

nov_18_grad + nov_18_race
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Race for November 18th
```{r}
# Table
nov_18_data %>%
  select(date, graduation_year) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Graduation Year") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race for November 18th
```{r}
# Table
nov_18_data %>%
  select(date, federal_race) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Federal Race") %>%
  kable_styling()
```
:::

```{r}
#| label: nov-18-extra-charac

nov_18_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(2, 49, 7, 44, 3, 48)
)

# Graph
ggplot(data = nov_18_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics for Novmber 18th
```{r}
# Table
nov_18_charac_table %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::

## December 2, 2022
```{r}
#| label: dec-2-dist

dec_2_data <- data %>%
  filter(date == "Dec 2nd") %>%
  select(date, topic, num_meetings, graduation_year, federal_race, iep, program_504, esl) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    graduation_year = as_factor(graduation_year), 
    federal_race = as_factor(federal_race)
    ) %>%
  filter(!is.na(federal_race), !is.na(graduation_year), !is.na(iep), !is.na(program_504), !is.na(esl))
```

```{r}
#| label: dec-2-num-meetings

# Graph
ggplot(data = dec_2_data, mapping = aes(x = num_meetings)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Number of Meetings Attended", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended for December 2nd
```{r}
# Table
dec_2_data %>%
  select(date, num_meetings) %>%
  count(num_meetings) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Number of Meetings Attended") %>%
  kable_styling()
```
:::

```{r}
#| label: dec-2-grad-year

# Graph
dec_2_grad <- ggplot(data = dec_2_data, mapping = aes(x = graduation_year, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

```{r}
#| label: dec-2-race

# Graph
dec_2_race <- ggplot(data = dec_2_data, mapping = aes(x = federal_race, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Race", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()

dec_2_grad + dec_2_race
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Race for December 2nd
```{r}
# Table
dec_2_data %>%
  select(date, graduation_year) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Graduation Year") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race for December 2nd
```{r}
# Table
dec_2_data %>%
  select(date, federal_race) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Federal Race") %>%
  kable_styling()
```
:::

```{r}
#| label: dec-2-extra-charac

dec_2_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(2, 46, 6, 42, 2, 46)
)

# Graph
ggplot(data = dec_2_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics for December 2nd
```{r}
# Table
dec_2_charac_table %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::

## January 27, 2023
```{r}
#| label: jan-27-dist

jan_27_data <- data %>%
  filter(date == "Jan 27th") %>%
  select(date, topic, num_meetings, graduation_year, federal_race, iep, program_504, esl) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    graduation_year = as_factor(graduation_year), 
    federal_race = as_factor(federal_race)
    ) %>%
  filter(!is.na(federal_race), !is.na(graduation_year), !is.na(iep), !is.na(program_504), !is.na(esl))
```

```{r}
#| label: jan-27-num-meetings

# Graph
ggplot(data = jan_27_data, mapping = aes(x = num_meetings)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Number of Meetings Attended", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended for January 27th
```{r}
# Table
jan_27_data %>%
  select(date, num_meetings) %>%
  count(num_meetings) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Number of Meetings Attended") %>%
  kable_styling()
```
:::

```{r}
#| label: jan-27-grad-year

# Graph
jan_27_grad <- ggplot(data = jan_27_data, mapping = aes(x = graduation_year, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

```{r}
#| label: jan-27-race

# Graph
jan_27_race <- ggplot(data = jan_27_data, mapping = aes(x = federal_race, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Race", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()

jan_27_grad + jan_27_race
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Race for January 27th
```{r}
# Table
jan_27_data %>%
  select(date, graduation_year) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Graduation Year") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race for January 27th
```{r}
# Table
jan_27_data %>%
  select(date, federal_race) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Federal Race") %>%
  kable_styling()
```
:::

```{r}
#| label: jan-27-extra-charac

jan_27_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(2, 42, 5, 39, 2, 42)
)

# Graph
ggplot(data = jan_27_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics for January 27th
```{r}
# Table
jan_27_charac_table %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::

## February 10, 2023
```{r}
#| label: feb-10-dist

feb_10_data <- data %>%
  filter(date == "Feb 10th") %>%
  select(date, topic, num_meetings, graduation_year, federal_race, iep, program_504, esl) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    graduation_year = as_factor(graduation_year), 
    federal_race = as_factor(federal_race)
    ) %>%
  filter(!is.na(federal_race), !is.na(graduation_year), !is.na(iep), !is.na(program_504), !is.na(esl))
```

```{r}
#| label: feb-10-num-meetings

# Graph
ggplot(data = feb_10_data, mapping = aes(x = num_meetings)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Number of Meetings Attended", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended for February 10th
```{r}
# Table
feb_10_data %>%
  select(date, num_meetings) %>%
  count(num_meetings) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Number of Meetings Attended") %>%
  kable_styling()
```
:::

```{r}
#| label: feb-10-grad-year

# Graph
feb_10_grad <- ggplot(data = feb_10_data, mapping = aes(x = graduation_year, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

```{r}
#| label: feb-10-race

# Graph
feb_10_race <- ggplot(data = feb_10_data, mapping = aes(x = federal_race, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Race", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()

feb_10_grad + feb_10_race
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Race for February 10th
```{r}
# Table
feb_10_data %>%
  select(date, graduation_year) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Graduation Year") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race for February 10th
```{r}
# Table
feb_10_data %>%
  select(date, federal_race) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Federal Race") %>%
  kable_styling()
```
:::

```{r}
#| label: feb-10-extra-charac

feb_10_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(1, 50, 6, 45, 2, 49)
)

# Graph
ggplot(data = feb_10_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics for February 10th
```{r}
# Table
feb_10_charac_table %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::

## February 24, 2023
```{r}
#| label: feb-24-dist

feb_24_data <- data %>%
  filter(date == "Feb 24th") %>%
  select(date, topic, num_meetings, graduation_year, federal_race, iep, program_504, esl) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    graduation_year = as_factor(graduation_year), 
    federal_race = as_factor(federal_race)
    ) %>%
  filter(!is.na(federal_race), !is.na(graduation_year), !is.na(iep), !is.na(program_504), !is.na(esl))
```

```{r}
#| label: feb-24-num-meetings

# Graph
ggplot(data = feb_24_data, mapping = aes(x = num_meetings)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Number of Meetings Attended", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended for February 24th
```{r}
# Table
feb_24_data %>%
  select(date, num_meetings) %>%
  count(num_meetings) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Number of Meetings Attended") %>%
  kable_styling()
```
:::

```{r}
#| label: feb-24-grad-year

# Graph
feb_24_grad <- ggplot(data = feb_24_data, mapping = aes(x = graduation_year, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

```{r}
#| label: feb-24-race

# Graph
feb_24_race <- ggplot(data = feb_24_data, mapping = aes(x = federal_race, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Race", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()

feb_24_grad + feb_24_race
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Race for February 24th
```{r}
# Table
feb_24_data %>%
  select(date, graduation_year) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Graduation Year") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race for February 24th
```{r}
# Table
feb_24_data %>%
  select(date, federal_race) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Federal Race") %>%
  kable_styling()
```
:::

```{r}
#| label: feb-24-extra-charac

feb_24_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(2, 46, 5, 43, 2, 46)
)

# Graph
ggplot(data = feb_24_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics for February 24th
```{r}
# Table
feb_24_charac_table %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::

## March 31, 2023
```{r}
#| label: mar-31-dist

mar_31_data <- data %>%
  filter(date == "Mar 31st") %>%
  select(date, topic, num_meetings, graduation_year, federal_race, iep, program_504, esl) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    graduation_year = as_factor(graduation_year), 
    federal_race = as_factor(federal_race)
    ) %>%
  filter(!is.na(federal_race), !is.na(graduation_year), !is.na(iep), !is.na(program_504), !is.na(esl))
```

```{r}
#| label: mar-31-num-meetings

# Graph
ggplot(data = mar_31_data, mapping = aes(x = num_meetings)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Number of Meetings Attended", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended for March 31st
```{r}
# Table
mar_31_data %>%
  select(date, num_meetings) %>%
  count(num_meetings) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Number of Meetings Attended") %>%
  kable_styling()
```
:::

```{r}
#| label: mar-31-grad-year

# Graph
mar_31_grad <- ggplot(data = mar_31_data, mapping = aes(x = graduation_year, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

```{r}
#| label: mar-31-race

# Graph
mar_31_race <- ggplot(data = mar_31_data, mapping = aes(x = federal_race, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Race", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()

mar_31_grad + mar_31_race
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Race for March 31st
```{r}
# Table
mar_31_data %>%
  select(date, graduation_year) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Graduation Year") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race for March 31st
```{r}
# Table
mar_31_data %>%
  select(date, federal_race) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Federal Race") %>%
  kable_styling()
```
:::

```{r}
#| label: mar-31-extra-charac

mar_31_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(2, 55, 5, 52, 2, 55)
)

# Graph
ggplot(data = mar_31_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics for March 31st
```{r}
# Table
mar_31_charac_table %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::

## April 14, 2023
```{r}
#| label: apr-14-dist

apr_14_data <- data %>%
  filter(date == "Apr 14th") %>%
  select(date, topic, num_meetings, graduation_year, federal_race, iep, program_504, esl) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    graduation_year = as_factor(graduation_year), 
    federal_race = as_factor(federal_race)
    ) %>%
  filter(!is.na(federal_race), !is.na(graduation_year), !is.na(iep), !is.na(program_504), !is.na(esl))
```

```{r}
#| label: apr-14-num-meetings

# Graph
ggplot(data = apr_14_data, mapping = aes(x = num_meetings)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Number of Meetings Attended", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended",
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended for April 14th
```{r}
# Table
apr_14_data %>%
  select(date, num_meetings) %>%
  count(num_meetings) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Number of Meetings Attended") %>%
  kable_styling()
```
:::

```{r}
#| label: apr-14-grad-year

# Graph
apr_14_grad <- ggplot(data = apr_14_data, mapping = aes(x = graduation_year, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

```{r}
#| label: apr-14-race

# Graph
apr_14_race <- ggplot(data = apr_14_data, mapping = aes(x = federal_race, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Race", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()

apr_14_grad + apr_14_race
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Race for April 14th
```{r}
# Table
apr_14_data %>%
  select(date, graduation_year) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Graduation Year") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race for April 14th
```{r}
# Table
apr_14_data %>%
  select(date, federal_race) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Federal Race") %>%
  kable_styling()
```
:::

```{r}
#| label: apr-14-extra-charac

apr_14_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(2, 38, 4, 36, 2, 38)
)

# Graph
ggplot(data = apr_14_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics for April 14th
```{r}
# Table
apr_14_charac_table %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::

## April 28, 2023
```{r}
#| label: apr-28-dist

apr_28_data <- data %>%
  filter(date == "Apr 28th") %>%
  select(date, topic, num_meetings, graduation_year, federal_race, iep, program_504, esl) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    graduation_year = as_factor(graduation_year), 
    federal_race = as_factor(federal_race)
    ) %>%
  filter(!is.na(federal_race), !is.na(graduation_year), !is.na(iep), !is.na(program_504), !is.na(esl))
```

```{r}
#| label: apr-28-num-meetings

# Graph
ggplot(data = apr_28_data, mapping = aes(x = num_meetings)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Number of Meetings Attended", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended for April 28th
```{r}
# Table
apr_28_data %>%
  select(date, num_meetings) %>%
  count(num_meetings) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Number of Meetings Attended") %>%
  kable_styling()
```
:::

```{r}
#| label: apr-28-grad-year

# Graph
apr_28_grad <- ggplot(data = apr_28_data, mapping = aes(x = graduation_year, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

```{r}
#| label: apr-28-race

# Graph
apr_28_race <- ggplot(data = apr_28_data, mapping = aes(x = federal_race, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Race", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()

apr_28_grad + apr_28_race
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Race for April 28th
```{r}
# Table
apr_28_data %>%
  select(date, graduation_year) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Graduation Year") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race for April 28th
```{r}
# Table
apr_28_data %>%
  select(date, federal_race) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Federal Race") %>%
  kable_styling()
```
:::

```{r}
#| label: apr-28-extra-charac

apr_28_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(NA, 9, 1, 8, NA, 9)
)

# Graph
ggplot(data = apr_28_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics for April 28th
```{r}
# Table
apr_28_charac_table %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::

## May 12, 2023
```{r}
#| label: may-12-dist

may_12_data <- data %>%
  filter(date == "May 12th") %>%
  select(date, topic, num_meetings, graduation_year, federal_race, iep, program_504, esl) %>%
  mutate(
    num_meetings = as_factor(num_meetings), 
    graduation_year = as_factor(graduation_year), 
    federal_race = as_factor(federal_race)
    ) %>%
  filter(!is.na(federal_race), !is.na(graduation_year), !is.na(iep), !is.na(program_504), !is.na(esl))
```

```{r}
#| label: may-12-num-meetings

# Graph
ggplot(data = may_12_data, mapping = aes(x = num_meetings)) + 
  geom_bar(color = "azure4", fill = "lightcyan2") + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Number of Meetings Attended", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Meetings Attended for May 12th
```{r}
# Table
may_12_data %>%
  select(date, num_meetings) %>%
  count(num_meetings) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Number of Meetings Attended") %>%
  kable_styling()
```
:::

```{r}
#| label: may-12-grad-year

# Graph
may_12_grad <- ggplot(data = may_12_data, mapping = aes(x = graduation_year, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

```{r}
#| label: may-12-race

# Graph
may_12_race <- ggplot(data = may_12_data, mapping = aes(x = federal_race, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +  
  labs(
    title = "Distribution By Race", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  theme_minimal()

may_12_grad + may_12_race
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Race for May 12th
```{r}
# Table
may_12_data %>%
  select(date, graduation_year) %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Graduation Year") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race for May 12th
```{r}
# Table
may_12_data %>%
  select(date, federal_race) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution By Federal Race") %>%
  kable_styling()
```
:::

```{r}
#| label: may-12-extra-charac

may_12_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(2, 44, 6, 40, 2, 44)
)

# Graph
ggplot(data = may_12_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics for May 12th
```{r}
# Table
may_12_charac_table %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::

# Attendance by Graduation Year

## Total Grade Distribution
```{r}
#| label: grade-dist

grade_distribution <- data %>%
  select(student_id, date, topic, num_meetings, graduation_year, federal_race) %>%
  filter(!is.na(graduation_year)) %>%
  mutate(
    graduation_year = as_factor(graduation_year), 
    num_meetings = as_factor(num_meetings), 
    federal_race = as_factor(federal_race)
    )

# Repeated
grade_repeat <- grade_distribution %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  )

## Graph
grade_repeat_graph <- ggplot(data = grade_repeat, mapping = aes(x = graduation_year, y = num_students, fill = graduation_year)) + 
  geom_col() + 
  geom_text(aes(label = num_students), position = position_stack(vjust = 0.5)) + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Graduation Year", 
    subtitle = "With Repeats",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()

# Unique
grade_unique <- grade_distribution %>%
  select(student_id, num_meetings, graduation_year, federal_race) %>%
  unique() %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  )

## Graph
grade_unique_graph <- ggplot(data = grade_unique, mapping = aes(x = graduation_year, y = num_students, fill = graduation_year)) + 
  geom_col() + 
  geom_text(aes(label = num_students), position = position_stack(vjust = 0.5)) + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Graduation Year", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Graduation Year", 
    y = "Number of Students"
    ) + 
  theme_minimal()

# Combining
grade_repeat_graph + grade_unique_graph
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Year of All Students (With Repeats)
```{r}
## Table
grade_repeat %>%
  kbl(caption = "Graduation Year of All Students (With Repeats)") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Year of All Students (Unique)
```{r}
## Table
grade_unique %>%
  kbl(caption = "Graduation Year of All Students (Unique)") %>%
  kable_styling()
```
:::

## Comparing Grade Distributions with ETHS
```{r}
#| label: compare-grade-dist

eths_grade <- tibble(
  graduation_year = c(2026, 2025, 2024, 2023), 
  num_students = c(914, 995, 876, 905), 
  prop = num_students / sum(num_students), 
  percent = prop * 100
) %>%
  mutate(program = "eths") %>%
  select(program, graduation_year, num_students, prop, percent) %>%
  mutate(graduation_year = as_factor(graduation_year))

wistem_grade <- data %>%
  select(name, student_id, graduation_year) %>%
  unique() %>%
  count(graduation_year) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  mutate(program = "wistem") %>%
  select(program, graduation_year, num_students, prop, percent) %>%
  arrange(desc(graduation_year)) %>%
  mutate(graduation_year = as_factor(graduation_year))

compare_grade_dist <- full_join(eths_grade, wistem_grade)

# Graphs
## WiSTEM
wistem_grade_dist <- ggplot(data = wistem_grade, mapping = aes(y = graduation_year, x = num_students, fill = graduation_year)) + 
  geom_col() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(aes(label = sprintf("%.2f%%", percent)), position = position_stack(vjust = 0.5), size = 3) + 
  labs(
    title = "WiSTEM Grade Distribution", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    y = "Graduation Year", 
    x = "Number of Students"
    ) + 
  theme_minimal()

## ETHS
eths_grade_dist <- ggplot(data = eths_grade, mapping = aes(y = graduation_year, x = num_students, fill = graduation_year)) + 
  geom_col() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(aes(label = sprintf("%.2f%%", percent)), position = position_stack(vjust = 0.5), size = 3) + 
  labs(
    title = "ETHS Grade Distribution", 
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    y = "Graduation Year", 
    x = "Number of Students"
    ) + 
  theme_minimal()

## Combining
wistem_grade_dist + eths_grade_dist
```

::: {.callout-note icon=false collapse="true"}
## Table for Comparing Grade Distributions Between WiSTEM and ETHS
```{r}
# Table
compare_grade_dist %>%
  kbl(caption = "Comparing Grade Distributions (Unique)") %>%
  kable_styling()
```
:::

## Graduation Year and Number of Meetings
```{r}
#| label: grade-num-meetings

grade_num_meetings <- grade_distribution %>%
  select(student_id, num_meetings, graduation_year, federal_race) %>%
  unique() %>%
  select(-student_id)

grade_num_meetings_table <- grade_distribution %>%
  select(student_id, num_meetings, graduation_year, federal_race) %>%
  unique() %>%
  select(-student_id, -federal_race) %>%
  group_by(graduation_year, num_meetings) %>%
  summarize(num_students = n())

grade_num_meetings_table <- pivot_wider(grade_num_meetings_table, names_from = graduation_year, values_from = num_students)

# Graph
ggplot(data = grade_num_meetings, mapping = aes(x = num_meetings, fill = graduation_year)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Graduation Year and Number of Meetings",
    subtitle = "Unique Students",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Year and Number of Meetings Attended
```{r}
# Table
grade_num_meetings_table %>%
  kbl(caption = "Graduation Year and Number of Meetings Attended (Unique)") %>%
  kable_styling()
```
:::

## Graduation Year and Federal Race
```{r}
#| label: grade-federal-race

grade_race <- grade_distribution %>%
  select(student_id, num_meetings, graduation_year, federal_race) %>%
  unique() %>%
  select(-student_id)

grade_race_table <- grade_distribution %>%
  select(student_id, num_meetings, graduation_year, federal_race) %>%
  unique() %>%
  select(-student_id, -num_meetings) %>%
  group_by(graduation_year, federal_race) %>%
  summarize(num_students = n()) %>%
  mutate(num_students = num_students)

# Graph
ggplot(data = grade_race, mapping = aes(x = federal_race, fill = graduation_year)) + 
  geom_bar(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Graduation Year and Federal Race",
    subtitle = "By All Federal Race Categories (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  theme_minimal()

# Only Two Categories
grade_race_two <- grade_distribution %>%
  select(student_id, num_meetings, graduation_year, federal_race) %>%
  unique() %>%
  select(-student_id)

grade_race_two$federal_race <- recode(grade_race_two$federal_race, "Asian" = "Non-White")
grade_race_two$federal_race <- recode(grade_race_two$federal_race, "Black" = "Non-White")
grade_race_two$federal_race <- recode(grade_race_two$federal_race, "LatinX" = "Non-White")
grade_race_two$federal_race <- recode(grade_race_two$federal_race, "T.M.O." = "Non-White")

grade_race_table_two <- grade_distribution %>%
  select(student_id, num_meetings, graduation_year, federal_race)

grade_race_table_two$federal_race <- recode(grade_race_table_two$federal_race, "Asian" = "Non-White")
grade_race_table_two$federal_race <- recode(grade_race_table_two$federal_race, "Black" = "Non-White")
grade_race_table_two$federal_race <- recode(grade_race_table_two$federal_race, "LatinX" = "Non-White")
grade_race_table_two$federal_race <- recode(grade_race_table_two$federal_race, "T.M.O." = "Non-White")

grade_race_table_two <- grade_race_table_two %>%
  unique() %>%
  select(-student_id, -num_meetings) %>%
  group_by(graduation_year, federal_race) %>%
  summarize(num_students = n()) %>%
  mutate(num_students = num_students)

## Graph
ggplot(data = grade_race_two, mapping = aes(x = federal_race, fill = graduation_year)) + 
  geom_bar(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Graduation Year and Federal Race",
    subtitle = "By White and Non-White Students (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Year and Federal Race (Simple)
```{r}
# Table
grade_race_table_wider <- pivot_wider(grade_race_table, names_from = federal_race, values_from = num_students) %>%
  select(graduation_year, White, Black, Asian, LatinX, T.M.O.)

grade_race_table_wider %>%
  kbl(caption = "Graduation Year and Federal Race (Unique)") %>%
  kable_styling()

grade_race_table_two_wider <- pivot_wider(grade_race_table_two, names_from = federal_race, values_from = num_students)

grade_race_table_two_wider %>%
  kbl(caption = "Graduation Year and Federal Race (Unique)") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Year and Federal Race (By Year)

::: {.callout-note icon=false collapse="true"}
## Table for 2023 Graduation Year and Federal Race
```{r}
# Table
grade_race_table %>%
  filter(graduation_year == "2023") %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "2023 Graduation Year and Federal Race (Unique)") %>%
  kable_styling()

grade_race_table_two %>%
  filter(graduation_year == "2023") %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "2023 Graduation Year and Federal Race (Unique)") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for 2024 Graduation Year and Federal Race
```{r}
# Table
grade_race_table %>%
  filter(graduation_year == "2024") %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "2024 Graduation Year and Federal Race (Unique)") %>%
  kable_styling()

grade_race_table_two %>%
  filter(graduation_year == "2024") %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "2024 Graduation Year and Federal Race (Unique)") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for 2025 Graduation Year and Federal Race
```{r}
# Table
grade_race_table %>%
  filter(graduation_year == "2025") %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "2025 Graduation Year and Federal Race (Unique)") %>%
  kable_styling()

grade_race_table_two %>%
  filter(graduation_year == "2025") %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "2025 Graduation Year and Federal Race (Unique)") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for 2026 Graduation Year and Federal Race
```{r}
# Table
grade_race_table %>%
  filter(graduation_year == "2026") %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "2026 Graduation Year and Federal Race (Unique)") %>%
  kable_styling()

grade_race_table_two %>%
  filter(graduation_year == "2026") %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  kbl(caption = "2026 Graduation Year and Federal Race (Unique)") %>%
  kable_styling()
```
:::

:::

## Graduation Year and Topic
```{r}
#| label: grade-topic

grade_topic <- grade_distribution %>%
  group_by(topic, graduation_year) %>%
  summarize(num_students = n()) %>%
  select(graduation_year, topic, num_students) %>%
  mutate(num_students = num_students)

# Graph 
ggplot(data = grade_topic, mapping = aes(x = topic, y = num_students, fill = graduation_year)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Graduation Year and Topic",
    subtitle = "With Repeats",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Year and Topic (Simple)
```{r}
# Table
grade_topic_table <- pivot_wider(grade_topic, names_from = topic, values_from = num_students)

grade_topic_table %>%
  kbl(caption = "Graduation Year and Topic (With Repeats)") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Graduation Year and Topic (By Year)

::: {.callout-note icon=false collapse="true"}
## Table for 2023 Graduation Year and Topic
```{r}
# Table
grade_topic %>%
  filter(graduation_year == "2023") %>%
  mutate(
    prop = num_students / (55 + 14 + 13), 
    percent = prop * 100
  ) %>%
  kbl(caption = "2023 Graduation Year and Topic (With Repeats)") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for 2024 Graduation Year and Topic
```{r}
# Table
grade_topic %>%
  filter(graduation_year == "2024") %>%
  mutate(
    prop = num_students / (101 + 26 + 11 + 28 + 1), 
    percent = prop * 100
  ) %>%
  kbl(caption = "2024 Graduation Year and Topic (With Repeats)") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for 2025 Graduation Year and Topic
```{r}
# Table
grade_topic %>%
  filter(graduation_year == "2025") %>%
  mutate(
    prop = num_students / (133 + 33 + 25 + 38 + 8), 
    percent = prop * 100
  ) %>%
  kbl(caption = "2025 Graduation Year and Topic (With Repeats)") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for 2026 Graduation Year and Topic
```{r}
# Table
grade_topic %>%
  filter(graduation_year == "2026") %>%
  mutate(
    prop = num_students / (80 + 23 + 10 + 29), 
    percent = prop * 100
  ) %>%
  kbl(caption = "2026 Graduation Year and Topic (With Repeats)") %>%
  kable_styling()
```
:::

:::

# Attendance by Federal Race

## Total Race Distribution

```{r}
#| label: total-race-dist

race_dist_unique <- data %>%
  select(federal_race, student_id, num_meetings) %>%
  unique() %>%
  select(-student_id) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  )

# Graph
ggplot(data = race_dist_unique, mapping = aes(x = federal_race, y = num_students, fill = federal_race)) +
  geom_col() + 
  scale_fill_manual(values = unique_colors) +
  geom_text(aes(label = paste0(round(percent, 1), "%")), position = position_stack(vjust = 0.5)) + 
  labs(
    title = "Federal Race Distribution", 
    subtitle = "By All Federal Race Categories (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  theme_minimal()

# Only Two Categories
race_dist_unique_two <- data %>%
  select(federal_race, student_id, num_meetings) %>%
  unique() %>%
  select(-student_id)

race_dist_unique_two$federal_race <- recode(race_dist_unique_two$federal_race, "Asian" = "Non-White")
race_dist_unique_two$federal_race <- recode(race_dist_unique_two$federal_race, "Black" = "Non-White")
race_dist_unique_two$federal_race <- recode(race_dist_unique_two$federal_race, "LatinX" = "Non-White")
race_dist_unique_two$federal_race <- recode(race_dist_unique_two$federal_race, "T.M.O." = "Non-White")
  
race_dist_unique_two <- race_dist_unique_two %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  )

## Graph
ggplot(data = race_dist_unique_two, mapping = aes(x = federal_race, y = num_students, fill = federal_race)) +
  geom_col() + 
  scale_fill_manual(values = unique_colors) +
  geom_text(aes(label = paste0(round(percent, 1), "%")), position = position_stack(vjust = 0.5)) + 
  labs(
    title = "Federal Race Distribution", 
    subtitle = "By White and Non-White Students (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Total Race Distribution
```{r}
# Table
race_dist_unique %>%
  kbl(caption = "Federal Race Distribution (Unique)") %>%
  kable_styling()

race_dist_unique_two %>%
  kbl(caption = "Federal Race Distribution With Only White and Non-White (Unique)") %>%
  kable_styling()
```
:::

## Race Distribution Without One-Timers
```{r}
#| label: race-dist-without-one-timers

race_without_one <- data %>%
  filter(num_meetings != 1) %>%
  select(federal_race, student_id, num_meetings) %>%
  unique() %>%
  select(-student_id) %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  )

# Graph 
ggplot(data = race_without_one, mapping = aes(x = federal_race, y = num_students, fill = federal_race)) +
  geom_col() + 
  scale_fill_manual(values = unique_colors) +
  geom_text(aes(label = paste0(round(percent, 1), "%")), position = position_stack(vjust = 0.5)) + 
  labs(
    title = "Federal Race Distribution (Without One-Timers)", 
    subtitle = "By All Federal Race Categories (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
  ) + 
  theme_minimal()

# Only Two Categories
race_without_one_two <- data %>%
  filter(num_meetings != 1) %>%
  select(federal_race, student_id, num_meetings) %>%
  unique() %>%
  select(-student_id)

race_without_one_two$federal_race <- recode(race_without_one_two$federal_race, "Asian" = "Non-White")
race_without_one_two$federal_race <- recode(race_without_one_two$federal_race, "Black" = "Non-White")
race_without_one_two$federal_race <- recode(race_without_one_two$federal_race, "LatinX" = "Non-White")
race_without_one_two$federal_race <- recode(race_without_one_two$federal_race, "T.M.O." = "Non-White")

race_without_one_two <- race_without_one_two %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  )

## Graph
ggplot(data = race_without_one_two, mapping = aes(x = federal_race, y = num_students, fill = federal_race)) +
  geom_col() + 
  scale_fill_manual(values = unique_colors) +
  geom_text(aes(label = paste0(round(percent, 1), "%")), position = position_stack(vjust = 0.5)) + 
  labs(
    title = "Federal Race Distribution (Without One-Timers)", 
    subtitle = "By White and Non-White Students (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
  ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Total Race Distribution Without One-Timers
```{r}
# Table
race_without_one %>%
  kbl(caption = "Federal Race Distribution Without One-Timers (Unique)") %>%
  kable_styling()

race_without_one_two %>%
  kbl(caption = "Federal Race Distribution Without One-Timers (Only White and Non-White; Unique)") %>%
  kable_styling()
```
:::

## Comparing Race Distributions with ETHS
```{r}
#| label: compare-race-dist

eths_race <- tibble(
  federal_race = c("White", "Asian", "Black", "LatinX", "T.M.O."),
  num_students = c(1640, 198, 902, 724, 154), 
  prop = num_students / sum(num_students), 
  percent = prop * 100
) %>%
  mutate(program = "eths") %>%
  select(program, federal_race, num_students, prop, percent)

wistem_race <- data %>%
  select(name, student_id, federal_race) %>%
  unique() %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  mutate(program = "wistem") %>%
  select(program, federal_race, num_students, prop, percent) %>%
  arrange(desc(federal_race))

compare_race_dist <- full_join(eths_race, wistem_race)

# Graphs
## WiSTEM
wistem_race_dist <- ggplot(data = wistem_race, mapping = aes(x = federal_race, y = num_students, fill = federal_race)) + 
  geom_col() + 
  scale_fill_manual(values = unique_colors) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  labs(
    title = "WiSTEM Race Distribution", 
    subtitle = "By All Federal Race Categories (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  theme_minimal()

## ETHS
eths_race_dist <- ggplot(data = eths_race, mapping = aes(x = federal_race, y = num_students, fill = federal_race)) + 
  geom_col() + 
  scale_fill_manual(values = unique_colors) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  labs(title = "ETHS Race Distribution", 
       subtitle = "By All Federal Race Categories (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
       x = "Federal Race", 
       y = "Number of Students"
       ) + 
  theme_minimal()

## Combining
wistem_race_dist + eths_race_dist
```

```{r}
#| label: compare-race-dist-two-cat

eths_race_two <- tibble(
  federal_race = c("White", "Non-White"),
  num_students = c(1640, 1978), 
  prop = num_students / sum(num_students), 
  percent = prop * 100
) %>%
  mutate(program = "eths") %>%
  select(program, federal_race, num_students, prop, percent)

wistem_race_two <- data %>%
  select(name, student_id, federal_race) %>%
  unique() 

wistem_race_two$federal_race <- recode(wistem_race_two$federal_race, "Asian" = "Non-White")
wistem_race_two$federal_race <- recode(wistem_race_two$federal_race, "Black" = "Non-White")
wistem_race_two$federal_race <- recode(wistem_race_two$federal_race, "LatinX" = "Non-White")
wistem_race_two$federal_race <- recode(wistem_race_two$federal_race, "T.M.O." = "Non-White")

wistem_race_two <- wistem_race_two %>%
  count(federal_race) %>%
  rename(num_students = n) %>%
  mutate(
    prop = num_students / sum(num_students), 
    percent = prop * 100
  ) %>%
  mutate(program = "wistem") %>%
  select(program, federal_race, num_students, prop, percent) %>%
  arrange(desc(federal_race))

compare_race_dist_two <- full_join(eths_race_two, wistem_race_two)

# Graphs
## WiSTEM
wistem_race_dist_two <- ggplot(data = wistem_race_two, mapping = aes(x = federal_race, y = num_students, fill = federal_race)) + 
  geom_col() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(aes(label = sprintf("%.2f%%", percent)), position = position_stack(vjust = 0.5)) + 
  labs(
    title = "WiSTEM Race Distribution", 
    subtitle = "By White and Non-White Students (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Federal Race", 
    y = "Number of Students"
    ) + 
  theme_minimal()

## ETHS
eths_race_dist_two <- ggplot(data = eths_race_two, mapping = aes(x = federal_race, y = num_students, fill = federal_race)) + 
  geom_col() + 
  scale_fill_manual(values = unique_colors) + 
  geom_text(aes(label = sprintf("%.2f%%", percent)), position = position_stack(vjust = 0.5)) + 
  labs(title = "ETHS Race Distribution", 
       subtitle = "By White and Non-White Students (Unique Students)",
       caption = "Source: WiSTEM 2022-2023",
       x = "Federal Race", 
       y = "Number of Students"
       ) + 
  theme_minimal()

## Combining
wistem_race_dist_two / eths_race_dist_two
```

::: {.callout-note icon=false collapse="true"}
## Table for Comparing Race Distributions Between WiSTEM and ETHS (All Categories)
```{r}
# Table
compare_race_dist %>%
  kbl(caption = "Comparing Race Distributions (All Federal Race Categories) (Unique)") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Comparing Race Distributions Between WiSTEM and ETHS (White and Non-White)
```{r}
# Table
compare_race_dist_two %>%
  kbl(caption = "Comparing Race Distributions (White and Non-White) (Unique)") %>%
  kable_styling()
```
:::

## Race and Number of Meetings
```{r}
#| label: race-and-num-meetings

race_distribution <- data %>%
  select(student_id, date, topic, num_meetings, graduation_year, federal_race) %>%
  mutate(
    graduation_year = as_factor(graduation_year), 
    num_meetings = as_factor(num_meetings), 
    federal_race = as_factor(federal_race)
    )

race_num_meetings <- race_distribution %>%
  select(student_id, num_meetings, graduation_year, federal_race) %>%
  unique() %>%
  select(-student_id, -graduation_year)

race_num_meetings_table <- race_num_meetings %>%
  group_by(federal_race, num_meetings) %>%
  summarize(num_students = n())

# Graph
race_num_meetings_graph <- ggplot(data = race_num_meetings, mapping = aes(x = num_meetings, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Federal Race and Number of Meetings",
    subtitle = "By All Federal Race Categories (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()

## Only Two Categories
race_num_meetings_two <- race_num_meetings

race_num_meetings_two$federal_race <- recode(race_num_meetings_two$federal_race, "Asian" = "Non-White")
race_num_meetings_two$federal_race <- recode(race_num_meetings_two$federal_race, "Black" = "Non-White")
race_num_meetings_two$federal_race <- recode(race_num_meetings_two$federal_race, "LatinX" = "Non-White")
race_num_meetings_two$federal_race <- recode(race_num_meetings_two$federal_race, "T.M.O." = "Non-White")

race_num_meetings_table_two <- race_num_meetings_two %>%
  group_by(federal_race, num_meetings) %>%
  summarize(num_students = n())

race_num_meetings_graph_two <- ggplot(data = race_num_meetings_two, mapping = aes(x = num_meetings, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Federal Race and Number of Meetings",
    subtitle = "By White and Non-White (Unique Students)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Number of Meetings Attended", 
    y = "Number of Students"
    ) + 
  theme_minimal()

race_num_meetings_graph
race_num_meetings_graph_two
```

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race and Number of Meeings Attended (All Categories)
```{r}
# Table
race_num_meetings_table %>%
  kbl(caption = "Race and Number of Meetings Attended (All Federal Race Categories) (Unique)") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race and Number of Meeings Attended (White and Non-White)
```{r}
# Table
race_num_meetings_table_two %>%
  kbl(caption = "Race and Number of Meetings Attended (White and Non-White) (Unique)") %>%
  kable_styling()
```
:::

## Race and Topic
```{r}
#| label: race-and-topic

race_topic <- race_distribution %>%
  select(federal_race, topic)

race_topic_table <- race_topic %>%
  group_by(federal_race, topic) %>%
  summarize(num_students = n())

# Graph
race_topic_graph <- ggplot(data = race_topic, mapping = aes(x = topic, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  labs(
    title = "Federal Race and Topic",
    subtitle = "By All Federal Race Categories (With Repeats)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Topic", 
    y = "Number of Students"
    ) + 
  theme_minimal()

## Only Two Categories
race_topic_two <- race_topic

race_topic_two$federal_race <- recode(race_topic_two$federal_race, "Asian" = "Non-White")
race_topic_two$federal_race <- recode(race_topic_two$federal_race, "Black" = "Non-White")
race_topic_two$federal_race <- recode(race_topic_two$federal_race, "LatinX" = "Non-White")
race_topic_two$federal_race <- recode(race_topic_two$federal_race, "T.M.O." = "Non-White")

race_topic_table_two <- race_topic_two %>%
  group_by(federal_race, topic) %>%
  summarize(num_students = n())

race_topic_graph_two <- ggplot(data = race_topic_two, mapping = aes(x = topic, fill = federal_race)) + 
  geom_bar() + 
  scale_fill_manual(values = unique_colors) + 
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  labs(
    title = "Federal Race and Topic",
    subtitle = "By White and Non-White (With Repeats)",
    caption = "Source: WiSTEM 2022-2023",
    x = "Topic", 
    y = "Number of Students"
    ) + 
  theme_minimal()

race_topic_graph
race_topic_graph_two
```

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race and Topic (All Categories)
```{r}
# Table
race_topic_table %>%
  kbl(caption = "Race and Topic (All Federal Race Categories) (Unique)") %>%
  kable_styling()
```
:::

::: {.callout-note icon=false collapse="true"}
## Table for Federal Race and Topic (White and Non-White)
```{r}
# Table
race_topic_table_two %>%
  kbl(caption = "Race and Topic (White and Non-White) (Unique)") %>%
  kable_styling()
```
:::

# Attendance by Additional Characteristics

## Of All Unique Students
```{r}
#| label: total-extra-charac

total_charac_table <- tibble(
  characteristic = c("IEP", "IEP", "504 Plan", "504 Plan", "ESL", "ESL"), 
  applicable = c("Yes", "No", "Yes", "No", "Yes", "No"), 
  num_students = c(6, 132, 20, 118, 6, 132)
)

# Graph
ggplot(data = total_charac_table, mapping = aes(x = applicable, y = num_students, fill = characteristic)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = unique_colors) + 
  labs(
    title = "Extra Characteristics of Attending Students", 
    subtitle = "Unique Students",
    caption = "Source: WiENG 2022-2023",
    x = "If It Applies to a Student", 
    y = "Number of Students"
    ) + 
  theme_minimal()
```

::: {.callout-note icon=false collapse="true"}
## Table for Additional Characteristics of All Unique Students
```{r}
# Table
total_charac_table %>%
  mutate(
    prop = num_students / 138, 
    percent = prop * 100
  ) %>%
  kbl(caption = "Attendance Distribution by Additional Characteristics") %>%
  kable_styling()
```
:::
