---
title: "WiENG 2022 - 2023"
subtitle: "Exit Slip Analyses"

format:
  html:
    toc: true
    embed-resources: true
    echo: false
    link-external-newwindow: true
execute:
  warning: false
  message: false

from: markdown+emoji  
editor: 
  markdown: 
    wrap: 72
---

```{r}
#| label: load-packages

library(tidyverse)
library(patchwork)
library(readr)
library(kableExtra)

set.seed(1968)
```

```{r}
#| label: load-data-set

data <- read_csv(file = "data/processed/wieng_exit_slips_clean.csv") %>%
  filter(!is.na(interesting), !is.na(included), !is.na(belong))

data$interesting <- factor(data$interesting, levels = c("Somewhat", "Fairly", "Very"))
data$included <- factor(data$included, levels = c("Neutral", "Agree", "Strongly agree"))
data$belong <- factor(data$belong, levels = c("Neutral", "Agree", "Strongly agree"))
```

# Background

**WiENG:** In total, there were _ overall WiENG meetings held throughout the 2022-2023 academic school year. However, there were _ meetings with attendance data and _ meetings with exit slip data. Some of these overlap in missing both attendance and exit slip data.

**Exit Slips Distribution:** Overall, there were 169 total exit slips collected over the course of the 2022-2023 academic school year. The graph and table below show the number of exit slips obtained for each of the _ meetings where exit slips were provided: 
```{r}
#| label: exit-slip-per-meeting

# Number per meeting
date_order <- read_csv(file = "data/processed/wieng_exit_slips_clean.csv") %>%
  filter(!is.na(date))
date_order$date <- factor(date_order$date, levels = c("May 12th", "May 5th", "Apr 28th", "Apr 14th", "Mar 10th", "Mar 3rd", "Feb 24th", "Feb 10th", "Feb 3rd", "Jan 27th", "Jan 20th", "Jan 13th", "Dec 16th", "Dec 2nd", "Nov 18th", "Nov 4th", "Oct 28th", "Oct 21st", "Oct 14th"))

# Graph
ggplot(data = date_order, mapping = aes(y = date)) + 
  geom_bar(color = "azure4", fill = "gainsboro") + 
  geom_text(stat='count', aes(label=..count..), position = position_stack(vjust = 0.9)) +
  labs(title = "Number of Exit Slips Per Meeting")

# Table
date_order %>%
  filter(!is.na(date)) %>%
  count(date) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  kbl(caption = "Number of Exit Slips Per Meeting") %>%
  kable_styling()
```

# Completion Rate

**Distribution:** 
```{r}
#| label: completion

# Completion Rate
attendance_data <- read_csv(file = "data/processed/wieng_attendance_clean.csv") %>%
  filter(!is.na(date))
attendance_data$date <- factor(attendance_data$date, levels = c("May 12th", "May 9th", "May 5th", "Apr 28th", "Apr 21st", "Apr 14th", "Mar 17th", "Mar 10th", "Mar 3rd", "Feb 24th", "Feb 17th", "Feb 10th", "Feb 3rd", "Jan 27th", "Jan 20th", "Dec 16th", "Dec 2nd", "Nov 18th", "Nov 4th", "Oct 28th", "Oct 21st", "Oct 14th"))

attendance_data <- attendance_data %>%
  filter(!is.na(date))

# Table
completion_rate <- data.frame (
  date  = c("May 12th", "May 5th", "Apr 28th", "Apr 14th", "Mar 10th", "Mar 3rd", "Feb 24th", "Feb 10th", "Feb 3rd", "Jan 27th", "Jan 20th", "Jan 13th", "Dec 16th", "Dec 2nd", "Nov 18th", "Nov 4th", "Oct 28th", "Oct 21st", "Oct 14th"),
  exit_slips = c(6, 4, 9, 7, 9, 8, 10, 8, 13, 11, 6, 13, 9, 9, 7, 14, 4, 11, 11), 
  attendance = c(9, 8, 9, 11, 11, 9, 11, 13, 11, 15, 8, NA, 13, 10, 11, 16, 4, 11, 9)
) %>%
  mutate(
    completion_prop = exit_slips / attendance, 
    completion_percent = completion_prop * 100
  )

completion_rate %>%
  kbl(caption = "Exit Slip Completion Rate Per Meeting") %>%
  kable_styling()
```

# Overall Distribution Per Category
## Question 1
**Question:** How interesting was today's meeting?

**Distribution:** 
```{r}
#| label: avg-interesting

# Graph
interesting_order <- read_csv(file = "data/processed/wieng_exit_slips_clean.csv") %>%
  filter(!is.na(interesting))
interesting_order$interesting <- factor(interesting_order$interesting, levels = c("Somewhat", "Fairly", "Very"))

percentage_data <- interesting_order %>%
  group_by(interesting) %>%
  summarize(percentage = n() / nrow(interesting_order) * 100)

ggplot(data = interesting_order, mapping = aes(x = interesting)) + 
  geom_bar(color = "azure4", fill = "gainsboro") + 
  geom_text(data = percentage_data, aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -1) +
  labs(title = "Distribution for interesting")

# Table
data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Distribution for interesting") %>%
  kable_styling()
```

## Question 2
**Question:** I feel included in WiSTEM. 

**Distribution:**
```{r}
#| label: avg-included

# Graph
included_order <- read_csv(file = "data/processed/wieng_exit_slips_clean.csv") %>%
  filter(!is.na(included))
included_order$included <- factor(included_order$included, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))

percentage_data <- included_order %>%
  group_by(included) %>%
  summarize(percentage = n() / nrow(included_order) * 100)

ggplot(data = included_order, mapping = aes(x = included)) + 
  geom_bar(color = "azure4", fill = "gainsboro") + 
  geom_text(data = percentage_data, aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) + 
  labs(title = "Distribution for included")

# Table
data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Distribution for included") %>%
  kable_styling()
```

## Question 3
**Question:** I belong in a STE(A)M community. 

**Distribution:** 
```{r}
#| label: avg-belong

# Graph
belong_order <- read_csv(file = "data/processed/wieng_exit_slips_clean.csv") %>%
  filter(!is.na(belong))
belong_order$belong <- factor(belong_order$belong, levels = c("Strongly disagree", "Neutral", "Agree", "Strongly agree"))

percentage_data <- belong_order %>%
  group_by(belong) %>%
  summarize(percentage = n() / nrow(belong_order) * 100)

ggplot(data = belong_order, mapping = aes(x = belong)) + 
  geom_bar(color = "azure4", fill = "gainsboro") + 
  geom_text(data = percentage_data, aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +  
  labs(title = "Distribution for belong")

# Table
data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Distribution for belong") %>%
  kable_styling()
```

# Distribution Per Meeting

## October 14, 2022
**Topic:** 

**Distribution:**   
```{r}
#| label: oct-14

oct_14_data <- data %>%
  filter(date == "Oct 14th")

# interesting
oct_14_interesting <- oct_14_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = oct_14_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Oct 14th Distribution for interesting")

oct_14_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Oct 14th Distribution for interesting") %>%
  kable_styling()

# included
oct_14_included <- oct_14_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = oct_14_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Oct 14th Distribution for included")

oct_14_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Oct 14th Distribution for included") %>%
  kable_styling()

# belong
oct_14_belong <- oct_14_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = oct_14_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Oct 14th Distribution for belong")

oct_14_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Oct 14th Distribution for belong") %>%
  kable_styling()
```

## October 21, 2022
**Topic:** 

**Distribution:** 
```{r}
#| label: oct-21

oct_21_data <- data %>%
  filter(date == "Oct 21st")

# interesting
oct_21_interesting <- oct_21_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = oct_21_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Oct 21st Distribution for interesting")

oct_21_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Oct 21st Distribution for interesting") %>%
  kable_styling()

# included
oct_21_included <- oct_21_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = oct_21_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Oct 21st Distribution for included")

oct_21_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Oct 21st Distribution for included") %>%
  kable_styling()

# belong
oct_21_belong <- oct_21_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = oct_21_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Oct 21st Distribution for belong")

oct_21_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Oct 21st Distribution for belong") %>%
  kable_styling()
```

## October 28, 2022
**Topic:** 

**Distribution:** 
```{r}
#| label: oct-28

oct_28_data <- data %>%
  filter(date == "Oct 28th")

# interesting
oct_28_interesting <- oct_28_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = oct_28_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Oct 28th Distribution for interesting")

oct_28_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Oct 28th Distribution for interesting") %>%
  kable_styling()

# included
oct_28_included <- oct_28_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = oct_28_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Oct 28th Distribution for included")

oct_28_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Oct 28th Distribution for included") %>%
  kable_styling()

# belong
oct_28_belong <- oct_28_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = oct_28_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Oct 28th Distribution for belong")

oct_28_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Oct 28th Distribution for belong") %>%
  kable_styling()
```

## November 4, 2022
**Topic:** 

**Distribution:**    
```{r}
#| label: nov-4

nov_4_data <- data %>%
  filter(date == "Nov 4th")

# interesting
nov_4_interesting <- nov_4_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = nov_4_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Nov 4th Distribution for interesting")

nov_4_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Nov 4th Distribution for interesting") %>%
  kable_styling()

# included
nov_4_included <- nov_4_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = nov_4_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Nov 4th Distribution for included")

nov_4_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Nov 4th Distribution for included") %>%
  kable_styling()

# belong
nov_4_belong <- nov_4_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = nov_4_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Nov 4th Distribution for belong")

nov_4_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Nov 4th Distribution for belong") %>%
  kable_styling()
```

## November 18, 2022
**Topic:** 

**Distribution:**    
```{r}
#| label: nov-18

nov_18_data <- data %>%
  filter(date == "Nov 18th")

# interesting
nov_18_interesting <- nov_18_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = nov_18_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Nov 18th Distribution for interesting")

nov_18_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Nov 18th Distribution for interesting") %>%
  kable_styling()

# included
nov_18_included <- nov_18_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = nov_18_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Nov 18th Distribution for included")

nov_18_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Nov 18th Distribution for included") %>%
  kable_styling()

# belong
nov_18_belong <- nov_18_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = nov_18_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Nov 18th Distribution for belong")

nov_18_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Nov 18th Distribution for belong") %>%
  kable_styling()
```

## December 2, 2022
**Topic:** 

**Distribution:** 
```{r}
#| label: dec-2

dec_2_data <- data %>%
  filter(date == "Dec 2nd")

# interesting
dec_2_interesting <- dec_2_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = dec_2_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Dec 2nd Distribution for interesting")

dec_2_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Dec 2nd Distribution for interesting") %>%
  kable_styling()

# included
dec_2_included <- dec_2_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = dec_2_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Dec 2nd Distribution for included")

dec_2_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Dec 2nd Distribution for included") %>%
  kable_styling()

# belong
dec_2_belong <- dec_2_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = dec_2_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Dec 2nd Distribution for belong")

dec_2_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Dec 2nd Distribution for belong") %>%
  kable_styling()
```

## December 16, 2022
**Topic:** 

**Distribution:** 
```{r}
#| label: dec-16

dec_16_data <- data %>%
  filter(date == "Dec 16th")

# interesting
dec_16_interesting <- dec_16_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = dec_16_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Dec 16th Distribution for interesting")

dec_16_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Dec 16th Distribution for interesting") %>%
  kable_styling()

# included
dec_16_included <- dec_16_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = dec_16_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Dec 16th Distribution for included")

dec_16_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Dec 16th Distribution for included") %>%
  kable_styling()

# belong
dec_16_belong <- dec_16_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = dec_16_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Dec 16th Distribution for belong")

dec_16_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Dec 16th Distribution for belong") %>%
  kable_styling()
```

## January 13, 2023
**Topic:** 

**Distribution:** 
```{r}
#| label: jan-13

jan_13_data <- data %>%
  filter(date == "Jan 13th")

# interesting
jan_13_interesting <- jan_13_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = jan_13_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Jan 13th Distribution for interesting")

jan_13_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Jan 13th Distribution for interesting") %>%
  kable_styling()

# included
jan_13_included <- jan_13_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = jan_13_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Jan 13th Distribution for included")

jan_13_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Jan 13th Distribution for included") %>%
  kable_styling()

# belong
jan_13_belong <- jan_13_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = jan_13_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Jan 13th Distribution for belong")

jan_13_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Jan 13th Distribution for belong") %>%
  kable_styling()
```

## January 20, 2023
**Topic:** 

**Distribution:** 
```{r}
#| label: jan-20

jan_20_data <- data %>%
  filter(date == "Jan 20th")

# interesting
jan_20_interesting <- jan_20_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = jan_20_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Jan 20th Distribution for interesting")

jan_20_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Jan 20th Distribution for interesting") %>%
  kable_styling()

# included
jan_20_included <- jan_20_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = jan_20_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Jan 20th Distribution for included")

jan_20_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Jan 20th Distribution for included") %>%
  kable_styling()

# belong
jan_20_belong <- jan_20_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = jan_20_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Jan 20th Distribution for belong")

jan_20_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Jan 20th Distribution for belong") %>%
  kable_styling()
```

## January 27, 2023
**Topic:** 

**Distribution:** 
```{r}
#| label: jan-27

jan_27_data <- data %>%
  filter(date == "Jan 27th")

# interesting
jan_27_interesting <- jan_27_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = jan_27_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Jan 27th Distribution for interesting")

jan_27_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Jan 27th Distribution for interesting") %>%
  kable_styling()

# included
jan_27_included <- jan_27_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = jan_27_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Jan 27th Distribution for included")

jan_27_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Jan 27th Distribution for included") %>%
  kable_styling()

# belong
jan_27_belong <- jan_27_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = jan_27_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Jan 27th Distribution for belong")

jan_27_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Jan 27th Distribution for belong") %>%
  kable_styling()
```

## February 3, 2023
**Topic:** 

**Distribution:** 
```{r}
#| label: feb-3

feb_3_data <- data %>%
  filter(date == "Feb 3rd")

# interesting
feb_3_interesting <- feb_3_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = feb_3_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Feb 3rd Distribution for interesting")

feb_3_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Feb 3rd Distribution for interesting") %>%
  kable_styling()

# included
feb_3_included <- feb_3_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = feb_3_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Feb 3rd Distribution for included")

feb_3_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Feb 3rd Distribution for included") %>%
  kable_styling()

# belong
feb_3_belong <- feb_3_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = feb_3_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Feb 3rd Distribution for belong")

feb_3_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Feb 3rd Distribution for belong") %>%
  kable_styling()
```

## February 10, 2023
**Topic:** 

**Distribution:** 
```{r}
#| label: feb-10

feb_10_data <- data %>%
  filter(date == "Feb 10th")

# interesting
feb_10_interesting <- feb_10_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = feb_10_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Feb 10th Distribution for interesting")

feb_10_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Feb 10th Distribution for interesting") %>%
  kable_styling()

# included
feb_10_included <- feb_10_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = feb_10_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Feb 10th Distribution for included")

feb_10_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Feb 10th Distribution for included") %>%
  kable_styling()

# belong
feb_10_belong <- feb_10_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = feb_10_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Feb 10th Distribution for belong")

feb_10_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Feb 10th Distribution for belong") %>%
  kable_styling()
```

## February 24, 2023
**Topic:** 

**Distribution:** 
```{r}
#| label: feb-24

feb_24_data <- data %>%
  filter(date == "Feb 24th")

# interesting
feb_24_interesting <- feb_24_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = feb_24_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Feb 24th Distribution for interesting")

feb_24_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Feb 24th Distribution for interesting") %>%
  kable_styling()

# included
feb_24_included <- feb_24_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = feb_24_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Feb 24th Distribution for included")

feb_24_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Feb 24th Distribution for included") %>%
  kable_styling()

# belong
feb_24_belong <- feb_24_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = feb_24_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Feb 24th Distribution for belong")

feb_24_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Feb 24th Distribution for belong") %>%
  kable_styling()
```

## March 3, 2023
**Topic:** 

**Distribution:** 
```{r}
#| label: mar-3

mar_3_data <- data %>%
  filter(date == "Mar 3rd")

# interesting
mar_3_interesting <- mar_3_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = mar_3_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Mar 3rd Distribution for interesting")

mar_3_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Mar 3rd Distribution for interesting") %>%
  kable_styling()

# included
mar_3_included <- mar_3_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = mar_3_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Mar 3rd Distribution for included")

mar_3_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Mar 3rd Distribution for included") %>%
  kable_styling()

# belong
mar_3_belong <- mar_3_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = mar_3_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Mar 3rd Distribution for belong")

mar_3_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Mar 3rd Distribution for belong") %>%
  kable_styling()
```

## March 10, 2023
**Topic:** 

**Distribution:** 
```{r}
#| label: mar-10

mar_10_data <- data %>%
  filter(date == "Mar 10th")

# interesting
mar_10_interesting <- mar_10_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = mar_10_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Mar 10th Distribution for interesting")

mar_10_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Mar 10th Distribution for interesting") %>%
  kable_styling()

# included
mar_10_included <- mar_10_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = mar_10_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Mar 10th Distribution for included")

mar_10_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Mar 10th Distribution for included") %>%
  kable_styling()

# belong
mar_10_belong <- mar_10_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = mar_10_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Mar 10th Distribution for belong")

mar_10_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Mar 10th Distribution for belong") %>%
  kable_styling()
```

## April 14, 2023
**Topic:** 

**Distribution:**  
```{r}
#| label: apr-14

apr_14_data <- data %>%
  filter(date == "Apr 14th")

# interesting
apr_14_interesting <- apr_14_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = apr_14_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Apr 14th Distribution for interesting")

apr_14_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Apr 14th Distribution for interesting") %>%
  kable_styling()

# included
apr_14_included <- apr_14_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = apr_14_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Apr 14th Distribution for included")

apr_14_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Apr 14th Distribution for included") %>%
  kable_styling()

# belong
apr_14_belong <- apr_14_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = apr_14_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Apr 14th Distribution for belong")

apr_14_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Apr 14th Distribution for belong") %>%
  kable_styling()
```

## April 28, 2023
**Topic:** 

**Distribution:**  
```{r}
#| label: apr-28

apr_28_data <- data %>%
  filter(date == "Apr 28th")

# interesting
apr_28_interesting <- apr_28_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = apr_28_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Apr 28th Distribution for interesting")

apr_28_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Apr 28th Distribution for interesting") %>%
  kable_styling()

# included
apr_28_included <- apr_28_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = apr_28_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Apr 28th Distribution for included")

apr_28_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Apr 28th Distribution for included") %>%
  kable_styling()

# belong
apr_28_belong <- apr_28_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = apr_28_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Apr 28th Distribution for belong")

apr_28_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Apr 28th Distribution for belong") %>%
  kable_styling()
```

## May 5, 2023
**Topic:** 

**Distribution:** 
```{r}
#| label: may-5

may_5_data <- data %>%
  filter(date == "May 5th")

# interesting
may_5_interesting <- may_5_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = may_5_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "May 5th Distribution for interesting")

may_5_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "May 5th Distribution for interesting") %>%
  kable_styling()

# included
may_5_included <- may_5_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = may_5_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "May 5th Distribution for included")

may_5_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "May 5th Distribution for included") %>%
  kable_styling()

# belong
may_5_belong <- may_5_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = may_5_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "May 5th Distribution for belong")

may_5_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "May 5th Distribution for belong") %>%
  kable_styling()
```

## May 12, 2023
**Topic:** 

**Distribution:** 
```{r}
#| label: may-12

may_12_data <- data %>%
  filter(date == "May 12th")

# interesting
may_12_interesting <- may_12_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = may_12_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "May 12th Distribution for interesting")

may_12_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "May 12th Distribution for interesting") %>%
  kable_styling()

# included
may_12_included <- may_12_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = may_12_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "May 12th Distribution for included")

may_12_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "May 12th Distribution for included") %>%
  kable_styling()

# belong
may_12_belong <- may_12_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = may_12_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "May 12th Distribution for belong")

may_12_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "May 12th Distribution for belong") %>%
  kable_styling()
```

# Distribution Per Topic

## Activity
**Distribution:**  
```{r}
#| label: activity-distribution

activity_data <- data %>%
  filter(topic == "Activity")

# interesting
activity_interesting <- activity_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = activity_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Activity Distribution for interesting")

activity_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Activity Distribution for interesting") %>%
  kable_styling()

# included
activity_included <- activity_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = activity_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Activity Distribution for included")

activity_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Activity Distribution for included") %>%
  kable_styling()

# belong
activity_belong <- activity_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = activity_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Activity Distribution for belong")

activity_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Activity Distribution for belong") %>%
  kable_styling()
```


## Guest Speaker

**Distribution:**  
```{r}
#| label: guest-distribution

guest_data <- data %>%
  filter(topic == "Guest Speaker")

# interesting
guest_interesting <- guest_data %>%
  group_by(interesting) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = guest_interesting, mapping = aes(x = interesting, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Guest Speaker Distribution for interesting")

guest_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Guest Speaker Distribution for interesting") %>%
  kable_styling()

# included
guest_included <- guest_data %>%
  group_by(included) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = guest_included, mapping = aes(x = included, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Guest Speaker Distribution for included")

guest_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Guest Speaker Distribution for included") %>%
  kable_styling()

# belong
guest_belong <- guest_data %>%
  group_by(belong) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = guest_belong, mapping = aes(x = belong, y = count)) + 
  geom_bar(color = "azure4", fill = "gainsboro", stat="identity") + 
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 4) +
  labs(title = "Guest Speaker Distribution for belong")

guest_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  kbl(caption = "Guest Speaker Distribution for belong") %>%
  kable_styling()
```
